Benchmark!!1

### 2021-02-15 paper/main.tex
more paper content

Philosophy: not necessarily the best
implementation in the world, but a reasonably good one, i.e. one we
can expect from an average student. Similar algorithm in various languages.

What we measure: run time of the algorithm only. Everything else
(reading data, building initial solution) is not measured. Currently
Julia, Javascript, Pypy, Numba also measure compilation time.

In order to represent a tour in heuristics we restrict ourselves to
variable-size vectors, since they are necessary in most algorithms for
vehicle routing, for instance to insert or delete a vertex from a
tour.
% This is the reason why we do
% not provide a C implementation. It is of course possible to
% implement variable-size vectors using fixed-size arrays and
% bookkeeping; however this stands directly against our stated purposes
% and philosophy. Moreover, implementing a bug-free, efficient version
% of variable-size vectors is unlikely to result in something better
% than existing libraries.
Inserting and deleting elements in a vector has linear worst-case time
complexity. However, for heuristics it is still usually a good idea to
use vectors rather than, say, linked lists, since neighborhood
exploration typically requires to evaluate many moves then perform
only one of these moves. The complexity of performing a move is thus
secondary and unlikely to be a performance bottleneck. Additionally,
performing certain moves can actually be more efficient using a
vector than using a linked list, e.g. inverting a subsequence.

\subsection{Limitations}
Benchmarks are by definition limited in scope; any given benchmark
measurement is only valid within a certain environment. In our case
such environmental factors include the choice of compilers, compiler
versions, operating system and CPU family. Therefore all results are
to be taken as indicators but not absolute truths. The intent of this
study is not to declare a language the winner because it is
consistently faster than others by a few percents, but rather to
assess what kind of performance losses can be expected by, for
example, using Python instead of C++. OR to assess what kind of
performance gains can be achieved by using a JIT compiler for Python.

>>>>

Philosophy: not necessarily the best
implementation in the world, but a reasonably good one, i.e. one we
can expect from an average student. Similar algorithm in various
languages. Use as few external libraries as possible, but use them if
needed.

\subsection{What we measure}
In all proposed benchmarks, we measure the CPU clock time of the
benchmarked algorithm. Every other task, such as reading input data or
constructing an initial solution for local search benchmarks, is not
measured. However if an auxilliary graph needs to be constructed every
time the algorithm is run, then we also measure the construction of
said auxilliary graph. This is the case for benchmarks \emph{maxflow}
and \emph{espprc}.

In general, compilation time is not measured. However, some
implementations do just-in-time (JIT) compilation, for example Julia,
JavaScript, Pypy, Numba and Java. In such cases, this JIT compilation time is
included in the running time of the algorithm. In general we measure
clock time, i.e. the CPU budget used by the algorithm. In the case of
JavaScript we measure wall time as we are not aware of any
way to measure clock time in JavaScript.

In order to represent a tour in heuristics we use variable-size
vectors, since they are necessary in most algorithms for 
vehicle routing, for instance to insert or delete a vertex from a
tour.
% This is the reason why we do
% not provide a C implementation. It is of course possible to
% implement variable-size vectors using fixed-size arrays and
% bookkeeping; however this stands directly against our stated purposes
% and philosophy. Moreover, implementing a bug-free, efficient version
% of variable-size vectors is unlikely to result in something better
% than existing libraries.
Inserting and deleting elements in a vector has linear worst-case time
complexity. However, for heuristics it is still usually a good idea to
use vectors rather than, say, linked lists, since neighborhood
exploration typically requires to evaluate many moves then perform
only one of these moves. The complexity of performing a move is thus
secondary and unlikely to be a performance bottleneck. Additionally,
performing certain moves can actually be more efficient using a
vector than using a linked list, e.g. inverting a subsequence.

\subsection{Limitations}
Benchmarks are by definition limited in scope; any given benchmark
measurement is only valid within a certain environment. In our case
such environmental factors include the choice of compilers, compiler
versions, operating system and CPU family. Therefore all results are
to be taken as indicators but not absolute truths. The intent of this
study is not to declare a language the winner because it is
consistently faster than others by a few percents, but rather to
assess what kind of performance losses can be expected by, for
example, using Python instead of C++. Another example is to assess what kind of
performance gains can be achieved by using a JIT compiler for Python.
